Representing Scenes as Light Fields for Real Time Rendering in Virtual Reality Display

### 2021-01-19 TOG/5-result.tex
snapshot

\section{Evaluation}
\label{sec:result}
% use one net to represent a complicated scene
% we still have other option for real-time, like streaming
\note{
Ablation studies for the network training/losses
Target scene | uniformly downsampled image | local foveated rendered image | network predicted images ---> at least 4 different scenes.
streaming time for 4-5 different scenes: full resolution vs our network prediction for “same data size”
image quality of rendered scene vs our network prediction for “same amount of streaming time”
User study results
Table on performance comparison, streaming time, PSNR, SSIM, etc
}%note
\subsection{User Study}
\label{sec:study:user}
\zh{(Jan 10) all the Qs are answered offline, will update the section soon.}

@@

\paragraph{Setup}
?? subjects (\warning{? females and ? males, $M=?$, $SD=?$}) participated in the study. They were not involved in the project previously. Each participant was asked to wear a HTC Vive Pro Eye headset during the experiment. The headset is connected to a Windows machine with \warning{Intel i9-7900X CPU @ 3.30 GHz}, 64GB RAM and one NVIDIA GTX 3080 graphics card. During the experiment, the participants wearing the headset explored our stimuli. We used the \textit{two-alternative forced choice} (2AFC) method for both of our studies.

\paragraph{Task: Our method v.s. NeRF v.s. Ground Truth}
We aim at collecting user's feedback in VR display. Each participant were provided with \warning{30?} trials where each trial consisted a foveated area indicator and a pair of two stimuli. We randomize the order of the pairs for counterbalancing. To control the images to be shown for each participant, we choose to render the results for all conditions on predefined gaze positions rather than passing user's real time gaze input to the system. We indicate the location of the foveated area to users in advance to all the conditions first. For each condition, participants were asked to report \zhtd{whether they think the rendered result is better}.

@@

\qisun{Here is what I think. The conditions, OURS, UNIFORM (i.e. downsampled), NERF could be described in the stimuli part. Then in the task paragraph, we simply compare any given pair of these 3 conditions.}
% \zh{no more down samples?}
\zh{no GT included?}

\paragraph{Results}
\begin{figure}[htb]
    \centering
    \includegraphics[width=0.96\linewidth]{example-image-a}
    \caption{The users' preference votes from our evaluation experiment.}
    \label{fig:results:2afc}
\end{figure}
The user preference votes are visualized in \autoref{fig:results:2afc}.
% apply binomial test
% or apply ANOVA, there is a value of votes for each condition and we want to know if there exists significant effects on different condition.

\paragraph{Discussion}

@@

\begin{figure*}[htb]
    \centering
    \begin{minipage}{0.32\linewidth} %full res
        \subfloat[]{\includegraphics[width=0.96\linewidth]{TOG/figs/gas_gt1.png}}

        \subfloat[]{\includegraphics[width=0.96\linewidth]{TOG/figs/mc_gt1.png}}

        \subfloat[]{\includegraphics[width=0.96\linewidth]{example-image-a}}
    \end{minipage}
    \begin{minipage}{0.32\linewidth} %ours
        \subfloat[]{\includegraphics[width=0.96\linewidth]{TOG/figs/gas_fovea_result1.png}}

        \subfloat[]{\includegraphics[width=0.96\linewidth]{TOG/figs/mc_fovea_result1.png}}

        \subfloat[]{\includegraphics[width=0.96\linewidth]{example-image-a}}
    \end{minipage}
    \begin{minipage}{0.32\linewidth} % NERF
        \subfloat[]{\includegraphics[width=0.96\linewidth]{example-image-a}}

        \subfloat[]{\includegraphics[width=0.96\linewidth]{example-image-a}}

        \subfloat[]{\includegraphics[width=0.96\linewidth]{example-image-a}}
    \end{minipage}

    \caption{Comparing our synthesis method with full resolution rendering and alternative solutions.}
    \label{fig:results:comparison}
\end{figure*}

\subsection{Spatial-Temporal Optimality}
%\zh{about streaming? network?}

>>>>

\section{Evaluation}
\label{sec:result}
% use one net to represent a complicated scene
% we still have other option for real-time, like streaming
\note{
Ablation studies for the network training/losses
Target scene | uniformly downsampled image | local foveated rendered image | network predicted images ---> at least 4 different scenes.
streaming time for 4-5 different scenes: full resolution vs our network prediction for “same data size”
image quality of rendered scene vs our network prediction for “same amount of streaming time”
User study results
Table on performance comparison, streaming time, PSNR, SSIM, etc
}%note
\subsection{User Study}
\label{sec:study:user}
% \zh{(Jan 10) all the Qs are answered offline, will update the section soon.}

@@

\paragraph{Setup}
?? users (\warning{? females and ? males, $M=?$, $SD=?$}) participated in the study. They were not involved in the project previously. Each participant was asked to wear a HTC Vive Pro Eye headset during the experiment.  During the experiment, the participants wearing the headset explored our stimuli. We used the \textit{two-alternative forced choice} (2AFC) method for both of our studies.

\paragraph{Task}
The task was a two-alternative-forced-choice (2AFC). 
Each participant were provided with \warning{30?} trials where each trial consisted a foveated area indicator and a pair of two stimuli. We randomize the order of the pairs for counterbalancing. To control the images to be shown for each participant, we choose to render the results for all conditions on predefined gaze positions rather than passing user's real time gaze input to the system. We indicate the location of the foveated area to users in advance to all the conditions first. For each condition, participants were instructed to indicate which of the two conditions appeared to be with higher quality.

@@

%\qisun{Here is what I think. The conditions, OURS, UNIFORM (i.e. downsampled), NERF could be described in the stimuli part. Then in the task paragraph, we simply compare any given pair of these 3 conditions.}
% \zh{no more down samples?}
%\zh{no GT included?}

\paragraph{Results and discussion}
\Cref{fig:results:2afc} plots the study results.

\begin{figure}[htb]
    \centering
    \includegraphics[width=0.96\linewidth]{example-image-a}
    \caption{The users' preference votes from our evaluation experiment.}
    \label{fig:results:2afc}
\end{figure}

% apply binomial test https://docs.scipy.org/doc/scipy/reference/generated/scipy.stats.binom_test.html
% or apply ANOVA, there is a value of votes for each condition and we want to know if there exists significant effects on different condition.

The results about indicated the similar perceptual quality between {\bf OURS} and {\bf GT}. However, the participants significantly observed the quality drop from {\bf NERF}.

To further validate the perceptual quality, we conducted measurements with objective metrics in the following section.

\begin{figure}
    \centering
    \subfloat[ANOVA on FWQI]{\includegraphics[width = 0.8\linewidth]{example-image-a}}

    \subfloat[FWQI gaze heatmap]{\includegraphics[width = 0.8\linewidth]{example-image-a}}
    \caption{Objective measurements on visual quality.}
    \label{fig:result:visual}
\end{figure}

\begin{figure*}[htb]
    \centering
    \begin{minipage}{0.32\linewidth} %full res
        \subfloat[]{\includegraphics[width=0.96\linewidth]{TOG/figs/gas_gt4.png}}

        \subfloat[]{\includegraphics[width=0.96\linewidth]{TOG/figs/mc_gt3.png}}

        \subfloat[]{\includegraphics[width=0.96\linewidth]{TOG/figs/bed_gt0.png}}
    \end{minipage}
    \begin{minipage}{0.32\linewidth} %ours
        \subfloat[]{\includegraphics[width=0.96\linewidth]{TOG/figs/gas_our4_inset.pdf}}

        \subfloat[]{\includegraphics[width=0.96\linewidth]{TOG/figs/mc_our3_inset.pdf}}

        \subfloat[]{\includegraphics[width=0.96\linewidth]{example-image-a}}               
    \end{minipage}
    \begin{minipage}{0.32\linewidth} % NERF
        \subfloat[]{\includegraphics[width=0.96\linewidth]{TOG/figs/gas_nerf4_inset.pdf}}

        \subfloat[]{\includegraphics[width=0.96\linewidth]{TOG/figs/mc_nerf3_inset.pdf}}

        \subfloat[]{\includegraphics[width=0.96\linewidth]{TOG/figs/bed_nerf0.png}}      
    \end{minipage}

    \caption{Comparing our synthesis method with full resolution (2nd column) rendering and NeRF (3rd column).}
    {\zh{add inset for 2nd and 3rd col}}
    \label{fig:results:comparison}
\end{figure*}

\begin{figure*}[htb]
    \centering
    \begin{minipage}{0.32\linewidth} %full res

        \subfloat[]{\includegraphics[width=0.96\linewidth]{TOG/figs/study_gt0.png}}
    \end{minipage}
    \begin{minipage}{0.32\linewidth} %ours

        \subfloat[]{\includegraphics[width=0.96\linewidth]{example-image-a}}                
    \end{minipage}
    \begin{minipage}{0.32\linewidth} % NERF

        \subfloat[]{\includegraphics[width=0.96\linewidth]{TOG/figs/study_nerf0.png}}        
    \end{minipage}

    \caption{Comparing our synthesis method with full resolution (2nd column) rendering and NeRF (3rd column) (Cont.).}
    {\zh{add inset for 2nd and 3rd col}}
    \label{fig:results:comparison2}
\end{figure*}

@@

\subsection{Spatial-Temporal Optimality}

% apply objective metric to Fig 7, aka different sample numbers

### 2021-01-19 TOG/teaser_fig.tex
snapshot

%\begin{figure}[htb]
\begin{teaserfigure}
  \centering
  \subfloat[scene representation]{
    \label{fig:teaser:scene}
    \includegraphics[width=0.45\linewidth]{TOG/figs/scene.pdf}
  }%subfloat
  \subfloat[latency]{
    \label{fig:teaser:latency}
    \includegraphics[width=0.25\linewidth]{example-image-a}
    % nerf: 108s/per infer
  }%subfloat
  \subfloat[quality]{
    \label{fig:teaser:quality}
    \includegraphics[width=0.25\linewidth]{example-image-a}
  }%subfloat
 \Caption{Illustration of our system.}
 {%
\subref{fig:teaser:scene} shows visualizes our active-viewing tailored scene representation.
Comparing with \protect\cite{mildenhall2020nerf}, \subref{fig:teaser:latency} shows our benefits of reduced latency.
As a zoom-in, \subref{fig:teaser:quality} compares our foveal quality preservation.
\qisun{Cross out half-half in  \subref{fig:teaser:hmd}. TODO for myself: I should make the background scene semi-transparent. Will do so soon.}
 }
 \label{fig:teaser}
%\end{figure}
\end{teaserfigure}

>>>>

%\begin{figure}[htb]
\begin{teaserfigure}
  \centering
  \subfloat[scene representation]{
    \label{fig:teaser:scene}
    % \includegraphics[height=4.5cm]{TOG/figs/scene.pdf}
    \includegraphics[height=4.5cm]{TOG/figs/teaser_1a.pdf} %try other colors a little bit
  }%subfloat
  \subfloat[latency]{
    \label{fig:teaser:latency}
    \includegraphics[height=4.5cm]{TOG/figs/teaser_1b_small.pdf}
    % \includegraphics[height=4.5cm]{TOG/figs/teaser.pdf}
    % nerf: 15+s/per infer
  }%subfloat
  \subfloat[foveal quality]{
    \label{fig:teaser:quality}
    \includegraphics[height=4.5cm]{TOG/figs/teaser_1c.pdf}
  }%subfloat
 \Caption{Illustration of our system.}
 {% 
\subref{fig:teaser:scene} shows visualizes our active-viewing tailored scene representation.
Comparing with \protect\cite{mildenhall2020nerf}, \subref{fig:teaser:latency} shows our benefits of reduced latency.
As a zoom-in, \subref{fig:teaser:quality} compares our foveal quality preservation.
\qisun{Cross out half-half in  \subref{fig:teaser:latency}. TODO for myself: I should make the background scene semi-transparent. Will do so soon.}
 }
 \label{fig:teaser}
%\end{figure}
\end{teaserfigure}
